\begin{thebibliography}


\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{}\fi
\expandafter\ifx\csname urllinklabel\endcsname\relax
  \def\urllinklabel{[LINK]}\fi
\expandafter\ifx\csname adsurllinklabel\endcsname\relax
  \def\adsurllinklabel{[ADS]}\fi

\bibitem[{Aaronson {et~al.}(1978)Aaronson, Cohen, Mould, \&
  Malkan}]{Aaronson:1978p3433}
Aaronson, M., Cohen, J.~G., Mould, J., \& Malkan, M. 1978, ApJ, 223, 824
 \href{http://adsabs.harvard.edu/cgi-bin/nph-data_query?bibcode=1978ApJ...223.%
.824A&link_type=ABSTRACT}{\urllinklabel}

\bibitem[{{Barrera-Ballesteros} {et~al.}(2014){Barrera-Ballesteros},
  {Falc{\'o}n-Barroso}, {Garc{\'{\i}}a-Lorenzo}, {van de Ven}, {Aguerri},
  {Mendez-Abreu}, {Spekkens}, {Lyubenova}, {S{\'a}nchez}, {Husemann}, {Mast},
  {Garc{\'{\i}}a-Benito}, {Iglesias-Paramo}, {Del Olmo}, {M{\'a}rquez},
  {Masegosa}, {Kehrig}, {Marino}, {Verdes-Montenegro}, {Ziegler}, {McIntosh},
  {Bland-Hawthorn}, {Walcher}, \& {Califa Collaboration}}]{jkbb14}
{Barrera-Ballesteros}, J.~K., {Falc{\'o}n-Barroso}, J.,
  {Garc{\'{\i}}a-Lorenzo}, B., {van de Ven}, G., {Aguerri}, J.~A.~L.,
  {Mendez-Abreu}, J., {Spekkens}, K., {Lyubenova}, M., {S{\'a}nchez}, S.~F.,
  {Husemann}, B., {Mast}, D., {Garc{\'{\i}}a-Benito}, R., {Iglesias-Paramo},
  J., {Del Olmo}, A., {M{\'a}rquez}, I., {Masegosa}, J., {Kehrig}, C.,
  {Marino}, R.~A., {Verdes-Montenegro}, L., {Ziegler}, B., {McIntosh}, D.~H.,
  {Bland-Hawthorn}, J., {Walcher}, C.~J., \& {Califa Collaboration}. 2014,
  \aap, 568, A70


\bibitem[{Bruzual \& Charlot(2003)}]{bc03}
Bruzual, G. \& Charlot, S. 2003, Mon. Not. R. Astron. Soc., 344, 1000
 \href{http://adsabs.harvard.edu/cgi-bin/nph-data_query?bibcode=2003MNRAS.344.%
1000B&link_type=ABSTRACT}{\urllinklabel}

\bibitem[{{Bundy} {et~al.}(2015){Bundy}, {Bershady}, {Law}, {Yan}, {Drory},
  {MacDonald}, {Wake}, {Cherinka}, {S{\'a}nchez-Gallego}, {Weijmans}, {Thomas},
  {Tremonti}, {Masters}, {Coccato}, {Diamond-Stanic}, {Arag{\'o}n-Salamanca},
  {Avila-Reese}, {Badenes}, {Falc{\'o}n-Barroso}, {Belfiore}, {Bizyaev},
  {Blanc}, {Bland-Hawthorn}, {Blanton}, {Brownstein}, {Byler}, {Cappellari},
  {Conroy}, {Dutton}, {Emsellem}, {Etherington}, {Frinchaboy}, {Fu}, {Gunn},
  {Harding}, {Johnston}, {Kauffmann}, {Kinemuchi}, {Klaene}, {Knapen},
  {Leauthaud}, {Li}, {Lin}, {Maiolino}, {Malanushenko}, {Malanushenko}, {Mao},
  {Maraston}, {McDermid}, {Merrifield}, {Nichol}, {Oravetz}, {Pan}, {Parejko},
  {Sanchez}, {Schlegel}, {Simmons}, {Steele}, {Steinmetz}, {Thanjavur},
  {Thompson}, {Tinker}, {van den Bosch}, {Westfall}, {Wilkinson}, {Wright},
  {Xiao}, \& {Zhang}}]{manga}
{Bundy}, K., {Bershady}, M.~A., {Law}, D.~R., {Yan}, R., {Drory}, N.,
  {MacDonald}, N., {Wake}, D.~A., {Cherinka}, B., {S{\'a}nchez-Gallego}, J.~R.,
  {Weijmans}, A.-M., {Thomas}, D., {Tremonti}, C., {Masters}, K., {Coccato},
  L., {Diamond-Stanic}, A.~M., {Arag{\'o}n-Salamanca}, A., {Avila-Reese}, V.,
  {Badenes}, C., {Falc{\'o}n-Barroso}, J., {Belfiore}, F., {Bizyaev}, D.,
  {Blanc}, G.~A., {Bland-Hawthorn}, J., {Blanton}, M.~R., {Brownstein}, J.~R.,
  {Byler}, N., {Cappellari}, M., {Conroy}, C., {Dutton}, A.~A., {Emsellem}, E.,
  {Etherington}, J., {Frinchaboy}, P.~M., {Fu}, H., {Gunn}, J.~E., {Harding},
  P., {Johnston}, E.~J., {Kauffmann}, G., {Kinemuchi}, K., {Klaene}, M.~A.,
  {Knapen}, J.~H., {Leauthaud}, A., {Li}, C., {Lin}, L., {Maiolino}, R.,
  {Malanushenko}, V., {Malanushenko}, E., {Mao}, S., {Maraston}, C.,
  {McDermid}, R.~M., {Merrifield}, M.~R., {Nichol}, R.~C., {Oravetz}, D.,
  {Pan}, K., {Parejko}, J.~K., {Sanchez}, S.~F., {Schlegel}, D., {Simmons}, A.,
  {Steele}, O., {Steinmetz}, M., {Thanjavur}, K., {Thompson}, B.~A., {Tinker},
  J.~L., {van den Bosch}, R.~C.~E., {Westfall}, K.~B., {Wilkinson}, D.,
  {Wright}, S., {Xiao}, T., \& {Zhang}, K. 2015, \apj, 798, 7


\bibitem[{{Calzetti}(2001)}]{calz01}
{Calzetti}, D. 2001, \pasp, 113, 1449


\bibitem[{{Cappellari} \& {Emsellem}(2004{\natexlab{a}})}]{cappe04}
{Cappellari}, M. \& {Emsellem}, E. 2004{\natexlab{a}}, \pasp, 116, 138


\bibitem[{{Cappellari} \& {Emsellem}(2004{\natexlab{b}})}]{cappellari04}
---. 2004{\natexlab{b}}, \pasp, 116, 138


\bibitem[{{Cardelli} {et~al.}(1989){Cardelli}, {Clayton}, \&
  {Mathis}}]{cardelli89}
{Cardelli}, J.~A., {Clayton}, G.~C., \& {Mathis}, J.~S. 1989, \apj, 345, 245


\bibitem[{Cardiel {et~al.}(2003)Cardiel, Gorgas, S{\'a}nchez-Bl{\'a}zquez,
  Cenarro, Pedraz, Bruzual, \& Klement}]{Cardiel:2003p3435}
Cardiel, N., Gorgas, J., S{\'a}nchez-Bl{\'a}zquez, P., Cenarro, A.~J., Pedraz,
  S., Bruzual, G., \& Klement, J. 2003, A\&A, 409, 511
 \href{http://adsabs.harvard.edu/cgi-bin/nph-data_query?bibcode=2003A\%2526A..%
.409..511C&link_type=ABSTRACT}{\urllinklabel}

\bibitem[{Chabrier(2003)}]{Chabrier:2003p3777}
Chabrier, G. 2003, PASP, 115, 763
 \href{http://adsabs.harvard.edu/cgi-bin/nph-data_query?bibcode=2003PASP..115.%
.763C&link_type=ABSTRACT}{\urllinklabel}

\bibitem[{Charlot \& Fall(2000)}]{Charlot:2000p3439}
Charlot, S. \& Fall, S.~M. 2000, ApJ, 539, 718
 \href{http://adsabs.harvard.edu/cgi-bin/nph-data_query?bibcode=2000ApJ...539.%
.718C&link_type=ABSTRACT}{\urllinklabel}

\bibitem[{{Cid Fernandes} {et~al.}(2014){Cid Fernandes}, {Gonz{\'a}lez
  Delgado}, {Garc{\'{\i}}a Benito}, {P{\'e}rez}, {de Amorim}, {S{\'a}nchez},
  {Husemann}, {Falc{\'o}n Barroso}, {L{\'o}pez-Fern{\'a}ndez},
  {S{\'a}nchez-Bl{\'a}zquez}, {Vale Asari}, {Vazdekis}, {Walcher}, \&
  {Mast}}]{cid-fernandes14}
{Cid Fernandes}, R., {Gonz{\'a}lez Delgado}, R.~M., {Garc{\'{\i}}a Benito}, R.,
  {P{\'e}rez}, E., {de Amorim}, A.~L., {S{\'a}nchez}, S.~F., {Husemann}, B.,
  {Falc{\'o}n Barroso}, J., {L{\'o}pez-Fern{\'a}ndez}, R.,
  {S{\'a}nchez-Bl{\'a}zquez}, P., {Vale Asari}, N., {Vazdekis}, A., {Walcher},
  C.~J., \& {Mast}, D. 2014, \aap, 561, A130


\bibitem[{{Cid Fernandes} {et~al.}(2005){Cid Fernandes}, {Mateus}, {Sodr{\'e}},
  {Stasi{\'n}ska}, \& {Gomes}}]{cid-fernandes05}
{Cid Fernandes}, R., {Mateus}, A., {Sodr{\'e}}, L., {Stasi{\'n}ska}, G., \&
  {Gomes}, J.~M. 2005, \mnras, 358, 363


\bibitem[{{Cid Fernandes} {et~al.}(2013){Cid Fernandes}, {P{\'e}rez},
  {Garc{\'{\i}}a Benito}, {Gonz{\'a}lez Delgado}, {de Amorim}, {S{\'a}nchez},
  {Husemann}, {Falc{\'o}n Barroso}, {S{\'a}nchez-Bl{\'a}zquez}, {Walcher}, \&
  {Mast}}]{cid-fernandes13}
{Cid Fernandes}, R., {P{\'e}rez}, E., {Garc{\'{\i}}a Benito}, R., {Gonz{\'a}lez
  Delgado}, R.~M., {de Amorim}, A.~L., {S{\'a}nchez}, S.~F., {Husemann}, B.,
  {Falc{\'o}n Barroso}, J., {S{\'a}nchez-Bl{\'a}zquez}, P., {Walcher}, C.~J.,
  \& {Mast}, D. 2013, \aap, 557, A86


\bibitem[{{Courteau} {et~al.}(2014){Courteau}, {Cappellari}, {de Jong},
  {Dutton}, {Emsellem}, {Hoekstra}, {Koopmans}, {Mamon}, {Maraston}, {Treu}, \&
  {Widrow}}]{court13}
{Courteau}, S., {Cappellari}, M., {de Jong}, R.~S., {Dutton}, A.~A.,
  {Emsellem}, E., {Hoekstra}, H., {Koopmans}, L.~V.~E., {Mamon}, G.~A.,
  {Maraston}, C., {Treu}, T., \& {Widrow}, L.~M. 2014, Reviews of Modern
  Physics, 86, 47


\bibitem[{{Croom} {et~al.}(2012){Croom}, {Lawrence}, {Bland-Hawthorn},
  {Bryant}, {Fogarty}, {Richards}, {Goodwin}, {Farrell}, {Miziarski}, {Heald},
  {Jones}, {Lee}, {Colless}, {Brough}, {Hopkins}, {Bauer}, {Birchall}, {Ellis},
  {Horton}, {Leon-Saval}, {Lewis}, {L{\'o}pez-S{\'a}nchez}, {Min}, {Trinh}, \&
  {Trowland}}]{sami}
{Croom}, S.~M., {Lawrence}, J.~S., {Bland-Hawthorn}, J., {Bryant}, J.~J.,
  {Fogarty}, L., {Richards}, S., {Goodwin}, M., {Farrell}, T., {Miziarski}, S.,
  {Heald}, R., {Jones}, D.~H., {Lee}, S., {Colless}, M., {Brough}, S.,
  {Hopkins}, A.~M., {Bauer}, A.~E., {Birchall}, M.~N., {Ellis}, S., {Horton},
  A., {Leon-Saval}, S., {Lewis}, G., {L{\'o}pez-S{\'a}nchez}, {\'A}.~R., {Min},
  S.-S., {Trinh}, C., \& {Trowland}, H. 2012, \mnras, 421, 872


\bibitem[{{Falc{\'o}n-Barroso} {et~al.}(2011){Falc{\'o}n-Barroso},
  {S{\'a}nchez-Bl{\'a}zquez}, {Vazdekis}, {Ricciardelli}, {Cardiel}, {Cenarro},
  {Gorgas}, \& {Peletier}}]{falc11}
{Falc{\'o}n-Barroso}, J., {S{\'a}nchez-Bl{\'a}zquez}, P., {Vazdekis}, A.,
  {Ricciardelli}, E., {Cardiel}, N., {Cenarro}, A.~J., {Gorgas}, J., \&
  {Peletier}, R.~F. 2011, \aap, 532, A95


\bibitem[{{Gerhard}(2003)}]{gerh2003}
{Gerhard}, O. in , The Mass of Galaxies at Low and High Redshift, ed.
  R.~{Bender}A.~{Renzini}, 62


\bibitem[{{Gil de Paz} \& {Madore}(2002)}]{gildepaz02}
{Gil de Paz}, A. \& {Madore}, B.~F. 2002, \aj, 123, 1864


\bibitem[{{Gonz{\'a}lez Delgado} {et~al.}(2005){Gonz{\'a}lez Delgado},
  {Cervi{\~n}o}, {Martins}, {Leitherer}, \& {Hauschildt}}]{rosa2005}
{Gonz{\'a}lez Delgado}, R.~M., {Cervi{\~n}o}, M., {Martins}, L.~P.,
  {Leitherer}, C., \& {Hauschildt}, P.~H. 2005, \mnras, 357, 945


\bibitem[{{Gonz{\'a}lez Delgado} {et~al.}(2015){Gonz{\'a}lez Delgado},
  {Garc{\'{\i}}a-Benito}, {P{\'e}rez}, {Cid Fernandes}, {de Amorim},
  {Cortijo-Ferrero}, {Lacerda}, {L{\'o}pez Fern{\'a}ndez}, {Vale-Asari},
  {S{\'a}nchez}, {Moll{\'a}}, {Ruiz-Lara}, {S{\'a}nchez-Bl{\'a}zquez},
  {Walcher}, {Alves}, {Aguerri}, {Bekerait{\'e}}, {Bland-Hawthorn}, {Galbany},
  {Gallazzi}, {Husemann}, {Iglesias-P{\'a}ramo}, {Kalinova},
  {L{\'o}pez-S{\'a}nchez}, {Marino}, {M{\'a}rquez}, {Masegosa}, {Mast},
  {M{\'e}ndez-Abreu}, {Mendoza}, {del Olmo}, {P{\'e}rez}, {Quirrenbach},
  {Zibetti}, \& {CALIFA collaboration}}]{rosa15a}
{Gonz{\'a}lez Delgado}, R.~M., {Garc{\'{\i}}a-Benito}, R., {P{\'e}rez}, E.,
  {Cid Fernandes}, R., {de Amorim}, A.~L., {Cortijo-Ferrero}, C., {Lacerda},
  E.~A.~D., {L{\'o}pez Fern{\'a}ndez}, R., {Vale-Asari}, N., {S{\'a}nchez},
  S.~F., {Moll{\'a}}, M., {Ruiz-Lara}, T., {S{\'a}nchez-Bl{\'a}zquez}, P.,
  {Walcher}, C.~J., {Alves}, J., {Aguerri}, J.~A.~L., {Bekerait{\'e}}, S.,
  {Bland-Hawthorn}, J., {Galbany}, L., {Gallazzi}, A., {Husemann}, B.,
  {Iglesias-P{\'a}ramo}, J., {Kalinova}, V., {L{\'o}pez-S{\'a}nchez}, A.~R.,
  {Marino}, R.~A., {M{\'a}rquez}, I., {Masegosa}, J., {Mast}, D.,
  {M{\'e}ndez-Abreu}, J., {Mendoza}, A., {del Olmo}, A., {P{\'e}rez}, I.,
  {Quirrenbach}, A., {Zibetti}, S., \& {CALIFA collaboration}. 2015, ArXiv
  e-prints


\bibitem[{{Gonz{\'a}lez Delgado} {et~al.}(2014){Gonz{\'a}lez Delgado},
  {P{\'e}rez}, {Cid Fernandes}, {Garc{\'{\i}}a-Benito}, {de Amorim},
  {S{\'a}nchez}, {Husemann}, {Cortijo-Ferrero}, {L{\'o}pez Fern{\'a}ndez},
  {S{\'a}nchez-Bl{\'a}zquez}, {Bekeraite}, {Walcher}, {Falc{\'o}n-Barroso},
  {Gallazzi}, {van de Ven}, {Alves}, {Bland-Hawthorn}, {Kennicutt}, {Kupko},
  {Lyubenova}, {Mast}, {Moll{\'a}}, {Marino}, {Quirrenbach}, {V{\'{\i}}lchez},
  \& {Wisotzki}}]{rosa14}
{Gonz{\'a}lez Delgado}, R.~M., {P{\'e}rez}, E., {Cid Fernandes}, R.,
  {Garc{\'{\i}}a-Benito}, R., {de Amorim}, A.~L., {S{\'a}nchez}, S.~F.,
  {Husemann}, B., {Cortijo-Ferrero}, C., {L{\'o}pez Fern{\'a}ndez}, R.,
  {S{\'a}nchez-Bl{\'a}zquez}, P., {Bekeraite}, S., {Walcher}, C.~J.,
  {Falc{\'o}n-Barroso}, J., {Gallazzi}, A., {van de Ven}, G., {Alves}, J.,
  {Bland-Hawthorn}, J., {Kennicutt}, R.~C., {Kupko}, D., {Lyubenova}, M.,
  {Mast}, D., {Moll{\'a}}, M., {Marino}, R.~A., {Quirrenbach}, A.,
  {V{\'{\i}}lchez}, J.~M., \& {Wisotzki}, L. 2014, \aap, 562, A47


\bibitem[{{Koleva} {et~al.}(2009){Koleva}, {Prugniel}, {Bouchard}, \&
  {Wu}}]{koleva2009}
{Koleva}, M., {Prugniel}, P., {Bouchard}, A., \& {Wu}, Y. 2009, \aap, 501, 1269


\bibitem[{{Le Borgne} {et~al.}(2003){Le Borgne}, {Bruzual}, {Pell{\'o}},
  {Lan{\c c}on}, {Rocca-Volmerange}, {Sanahuja}, {Schaerer}, {Soubiran}, \&
  {V{\'{\i}}lchez-G{\'o}mez}}]{stelib}
{Le Borgne}, J.-F., {Bruzual}, G., {Pell{\'o}}, R., {Lan{\c c}on}, A.,
  {Rocca-Volmerange}, B., {Sanahuja}, B., {Schaerer}, D., {Soubiran}, C., \&
  {V{\'{\i}}lchez-G{\'o}mez}, R. 2003, \aap, 402, 433


\bibitem[{{MacArthur} {et~al.}(2004){MacArthur}, {Courteau}, {Bell}, \&
  {Holtzman}}]{macarthur+04}
{MacArthur}, L.~A., {Courteau}, S., {Bell}, E., \& {Holtzman}, J.~A. 2004,
  \apjs, 152, 175


\bibitem[{{MacArthur} {et~al.}(2009){MacArthur}, {Gonz{\'a}lez}, \&
  {Courteau}}]{macarthur2009}
{MacArthur}, L.~A., {Gonz{\'a}lez}, J.~J., \& {Courteau}, S. 2009, \mnras, 395,
  28


\bibitem[{{Maraston}(2005)}]{mar05}
{Maraston}, C. 2005, \mnras, 362, 799


\bibitem[{{Maraston} \& {Str{\"o}mb{\"a}ck}(2011)}]{mar11}
{Maraston}, C. \& {Str{\"o}mb{\"a}ck}, G. 2011, \mnras, 418, 2785


\bibitem[{{M{\'a}rmol-Queralt{\'o}} {et~al.}(2011){M{\'a}rmol-Queralt{\'o}},
  {S{\'a}nchez}, {Marino}, {Mast}, {Viironen}, {Gil de Paz},
  {Iglesias-P{\'a}ramo}, {Rosales-Ortega}, \& {Vilchez}}]{marmol-queralto11}
{M{\'a}rmol-Queralt{\'o}}, E., {S{\'a}nchez}, S.~F., {Marino}, R.~A., {Mast},
  D., {Viironen}, K., {Gil de Paz}, A., {Iglesias-P{\'a}ramo}, J.,
  {Rosales-Ortega}, F.~F., \& {Vilchez}, J.~M. 2011, \aap, 534, A8


\bibitem[{{Martins} {et~al.}(2005){Martins}, {Gonz{\'a}lez Delgado},
  {Leitherer}, {Cervi{\~n}o}, \& {Hauschildt}}]{martins05}
{Martins}, L.~P., {Gonz{\'a}lez Delgado}, R.~M., {Leitherer}, C.,
  {Cervi{\~n}o}, M., \& {Hauschildt}, P. 2005, \mnras, 358, 49


\bibitem[{Oconnell(1976)}]{Oconnell:1976p3432}
Oconnell, R.~W. 1976, ApJ, 206, 370
 \href{http://adsabs.harvard.edu/cgi-bin/nph-data_query?bibcode=1976ApJ...206.%
.370O&link_type=ABSTRACT}{\urllinklabel}

\bibitem[{{Ocvirk} {et~al.}(2006){Ocvirk}, {Pichon}, {Lan{\c c}on}, \&
  {Thi{\'e}baut}}]{ocvrik2006}
{Ocvirk}, P., {Pichon}, C., {Lan{\c c}on}, A., \& {Thi{\'e}baut}, E. 2006,
  \mnras, 365, 46


\bibitem[{{Panter} {et~al.}(2003){Panter}, {Heavens}, \& {Jimenez}}]{pant2003}
{Panter}, B., {Heavens}, A.~F., \& {Jimenez}, R. 2003, \mnras, 343, 1145


\bibitem[{{Papaderos} {et~al.}(2013){Papaderos}, {Gomes}, {V{\'{\i}}lchez},
  {Kehrig}, {Lehnert}, {Ziegler}, {S{\'a}nchez}, {Husemann}, {Monreal-Ibero},
  {Garc{\'{\i}}a-Benito}, {Bland-Hawthorn}, {Cortijo-Ferrero}, {de
  Lorenzo-C{\'a}ceres}, {del Olmo}, {Falc{\'o}n-Barroso}, {Galbany},
  {Iglesias-P{\'a}ramo}, {L{\'o}pez-S{\'a}nchez}, {Marquez}, {Moll{\'a}},
  {Mast}, {van de Ven}, \& {Wisotzki}}]{papa13}
{Papaderos}, P., {Gomes}, J.~M., {V{\'{\i}}lchez}, J.~M., {Kehrig}, C.,
  {Lehnert}, M.~D., {Ziegler}, B., {S{\'a}nchez}, S.~F., {Husemann}, B.,
  {Monreal-Ibero}, A., {Garc{\'{\i}}a-Benito}, R., {Bland-Hawthorn}, J.,
  {Cortijo-Ferrero}, C., {de Lorenzo-C{\'a}ceres}, A., {del Olmo}, A.,
  {Falc{\'o}n-Barroso}, J., {Galbany}, L., {Iglesias-P{\'a}ramo}, J.,
  {L{\'o}pez-S{\'a}nchez}, {\'A}.~R., {Marquez}, I., {Moll{\'a}}, M., {Mast},
  D., {van de Ven}, G., \& {Wisotzki}, L. 2013, \aap, 555, L1


\bibitem[{{P{\'e}rez} {et~al.}(2013){P{\'e}rez}, {Cid Fernandes}, {Gonz{\'a}lez
  Delgado}, {Garc{\'{\i}}a-Benito}, {S{\'a}nchez}, {Husemann}, {Mast},
  {Rod{\'o}n}, {Kupko}, {Backsmann}, {de Amorim}, {van de Ven}, {Walcher},
  {Wisotzki}, {Cortijo-Ferrero}, \& {CALIFA Collaboration}}]{eperez13}
{P{\'e}rez}, E., {Cid Fernandes}, R., {Gonz{\'a}lez Delgado}, R.~M.,
  {Garc{\'{\i}}a-Benito}, R., {S{\'a}nchez}, S.~F., {Husemann}, B., {Mast}, D.,
  {Rod{\'o}n}, J.~R., {Kupko}, D., {Backsmann}, N., {de Amorim}, A.~L., {van de
  Ven}, G., {Walcher}, J., {Wisotzki}, L., {Cortijo-Ferrero}, C., \& {CALIFA
  Collaboration}. 2013, \apjl, 764, L1


\bibitem[{{Rix} \& {White}(1992)}]{rix92}
{Rix}, H.-W. \& {White}, S.~D.~M. 1992, \mnras, 254, 389


\bibitem[{{Rosales-Ortega} {et~al.}(2010){Rosales-Ortega}, {Kennicutt},
  {S{\'a}nchez}, {D{\'{\i}}az}, {Pasquali}, {Johnson}, \&
  {Hao}}]{rosales-ortega10}
{Rosales-Ortega}, F.~F., {Kennicutt}, R.~C., {S{\'a}nchez}, S.~F.,
  {D{\'{\i}}az}, A.~I., {Pasquali}, A., {Johnson}, B.~D., \& {Hao}, C.~N. 2010,
  \mnras, 405, 735


\bibitem[{Salpeter(1955)}]{Salpeter:1955p3438}
Salpeter, E.~E. 1955, ApJ, 121, 161
 \href{http://adsabs.harvard.edu/cgi-bin/nph-data_query?bibcode=1955ApJ...121.%
.161S&link_type=ABSTRACT}{\urllinklabel}

\bibitem[{{S{\'a}nchez}(2006a)}]{sanchez06a}
{S{\'a}nchez}, S.~F. 2006a, Astronomische Nachrichten, 327, 850


\bibitem[{{S{\'a}nchez} {et~al.}(2007a){S{\'a}nchez}, {Aceituno}, {Thiele},
  {P{\'e}rez-Ram{\'{\i}}rez}, \& {Alves}}]{sanchez07a}
{S{\'a}nchez}, S.~F., {Aceituno}, J., {Thiele}, U., {P{\'e}rez-Ram{\'{\i}}rez},
  D., \& {Alves}, J. 2007a, \pasp, 119, 1186


\bibitem[{{S{\'a}nchez} {et~al.}(2007b){S{\'a}nchez}, {Cardiel}, {Verheijen},
  {Pedraz}, \& {Covone}}]{sanchez07b}
{S{\'a}nchez}, S.~F., {Cardiel}, N., {Verheijen}, M.~A.~W., {Pedraz}, S., \&
  {Covone}, G. 2007b, \mnras, 376, 125


\bibitem[{{S{\'a}nchez} {et~al.}(2006b){S{\'a}nchez}, {Garc{\'{\i}}a-Lorenzo},
  {Jahnke}, {Mediavilla}, {Gonz{\'a}lez-Serrano}, {Christensen}, \&
  {Wisotzki}}]{sanchez06b}
{S{\'a}nchez}, S.~F., {Garc{\'{\i}}a-Lorenzo}, B., {Jahnke}, K., {Mediavilla},
  E., {Gonz{\'a}lez-Serrano}, J.~I., {Christensen}, L., \& {Wisotzki}, L.
  2006b, \nar, 49, 501


\bibitem[{{S{\'a}nchez} {et~al.}(2012{\natexlab{a}}){S{\'a}nchez}, {Kennicutt},
  {Gil de Paz}, {van de Ven}, {V{\'{\i}}lchez}, {Wisotzki}, {Walcher}, {Mast},
  {Aguerri}, {Albiol-P{\'e}rez}, {Alonso-Herrero}, {Alves}, {Bakos},
  {Bart{\'a}kov{\'a}}, {Bland-Hawthorn}, {Boselli}, {Bomans},
  {Castillo-Morales}, {Cortijo-Ferrero}, {de Lorenzo-C{\'a}ceres}, {Del Olmo},
  {Dettmar}, {D{\'{\i}}az}, {Ellis}, {Falc{\'o}n-Barroso}, {Flores},
  {Gallazzi}, {Garc{\'{\i}}a-Lorenzo}, {Gonz{\'a}lez Delgado}, {Gruel},
  {Haines}, {Hao}, {Husemann}, {Igl{\'e}sias-P{\'a}ramo}, {Jahnke}, {Johnson},
  {Jungwiert}, {Kalinova}, {Kehrig}, {Kupko}, {L{\'o}pez-S{\'a}nchez},
  {Lyubenova}, {Marino}, {M{\'a}rmol-Queralt{\'o}}, {M{\'a}rquez}, {Masegosa},
  {Meidt}, {Mendez-Abreu}, {Monreal-Ibero}, {Montijo}, {Mour{\~a}o},
  {Palacios-Navarro}, {Papaderos}, {Pasquali}, {Peletier}, {P{\'e}rez},
  {P{\'e}rez}, {Quirrenbach}, {Rela{\~n}o}, {Rosales-Ortega}, {Roth},
  {Ruiz-Lara}, {S{\'a}nchez-Bl{\'a}zquez}, {Sengupta}, {Singh}, {Stanishev},
  {Trager}, {Vazdekis}, {Viironen}, {Wild}, {Zibetti}, \&
  {Ziegler}}]{sanchez12a}
{S{\'a}nchez}, S.~F., {Kennicutt}, R.~C., {Gil de Paz}, A., {van de Ven}, G.,
  {V{\'{\i}}lchez}, J.~M., {Wisotzki}, L., {Walcher}, C.~J., {Mast}, D.,
  {Aguerri}, J.~A.~L., {Albiol-P{\'e}rez}, S., {Alonso-Herrero}, A., {Alves},
  J., {Bakos}, J., {Bart{\'a}kov{\'a}}, T., {Bland-Hawthorn}, J., {Boselli},
  A., {Bomans}, D.~J., {Castillo-Morales}, A., {Cortijo-Ferrero}, C., {de
  Lorenzo-C{\'a}ceres}, A., {Del Olmo}, A., {Dettmar}, R.-J., {D{\'{\i}}az},
  A., {Ellis}, S., {Falc{\'o}n-Barroso}, J., {Flores}, H., {Gallazzi}, A.,
  {Garc{\'{\i}}a-Lorenzo}, B., {Gonz{\'a}lez Delgado}, R., {Gruel}, N.,
  {Haines}, T., {Hao}, C., {Husemann}, B., {Igl{\'e}sias-P{\'a}ramo}, J.,
  {Jahnke}, K., {Johnson}, B., {Jungwiert}, B., {Kalinova}, V., {Kehrig}, C.,
  {Kupko}, D., {L{\'o}pez-S{\'a}nchez}, {\'A}.~R., {Lyubenova}, M., {Marino},
  R.~A., {M{\'a}rmol-Queralt{\'o}}, E., {M{\'a}rquez}, I., {Masegosa}, J.,
  {Meidt}, S., {Mendez-Abreu}, J., {Monreal-Ibero}, A., {Montijo}, C.,
  {Mour{\~a}o}, A.~M., {Palacios-Navarro}, G., {Papaderos}, P., {Pasquali}, A.,
  {Peletier}, R., {P{\'e}rez}, E., {P{\'e}rez}, I., {Quirrenbach}, A.,
  {Rela{\~n}o}, M., {Rosales-Ortega}, F.~F., {Roth}, M.~M., {Ruiz-Lara}, T.,
  {S{\'a}nchez-Bl{\'a}zquez}, P., {Sengupta}, C., {Singh}, R., {Stanishev}, V.,
  {Trager}, S.~C., {Vazdekis}, A., {Viironen}, K., {Wild}, V., {Zibetti}, S.,
  \& {Ziegler}, B. 2012{\natexlab{a}}, \aap, 538, A8


\bibitem[{{S{\'a}nchez} {et~al.}(2013){S{\'a}nchez}, {Rosales-Ortega},
  {Jungwiert}, {Iglesias-P{\'a}ramo}, {V{\'{\i}}lchez}, {Marino}, {Walcher},
  {Husemann}, {Mast}, {Monreal-Ibero}, {Cid Fernandes}, {P{\'e}rez},
  {Gonz{\'a}lez Delgado}, {Garc{\'{\i}}a-Benito}, {Galbany}, {van de Ven},
  {Jahnke}, {Flores}, {Bland-Hawthorn}, {L{\'o}pez-S{\'a}nchez}, {Stanishev},
  {Miralles-Caballero}, {D{\'{\i}}az}, {S{\'a}nchez-Blazquez}, {Moll{\'a}},
  {Gallazzi}, {Papaderos}, {Gomes}, {Gruel}, {P{\'e}rez}, {Ruiz-Lara},
  {Florido}, {de Lorenzo-C{\'a}ceres}, {Mendez-Abreu}, {Kehrig}, {Roth},
  {Ziegler}, {Alves}, {Wisotzki}, {Kupko}, {Quirrenbach}, {Bomans}, \& {Califa
  Collaboration}}]{sanchez13}
{S{\'a}nchez}, S.~F., {Rosales-Ortega}, F.~F., {Jungwiert}, B.,
  {Iglesias-P{\'a}ramo}, J., {V{\'{\i}}lchez}, J.~M., {Marino}, R.~A.,
  {Walcher}, C.~J., {Husemann}, B., {Mast}, D., {Monreal-Ibero}, A., {Cid
  Fernandes}, R., {P{\'e}rez}, E., {Gonz{\'a}lez Delgado}, R.,
  {Garc{\'{\i}}a-Benito}, R., {Galbany}, L., {van de Ven}, G., {Jahnke}, K.,
  {Flores}, H., {Bland-Hawthorn}, J., {L{\'o}pez-S{\'a}nchez}, A.~R.,
  {Stanishev}, V., {Miralles-Caballero}, D., {D{\'{\i}}az}, A.~I.,
  {S{\'a}nchez-Blazquez}, P., {Moll{\'a}}, M., {Gallazzi}, A., {Papaderos}, P.,
  {Gomes}, J.~M., {Gruel}, N., {P{\'e}rez}, I., {Ruiz-Lara}, T., {Florido}, E.,
  {de Lorenzo-C{\'a}ceres}, A., {Mendez-Abreu}, J., {Kehrig}, C., {Roth},
  M.~M., {Ziegler}, B., {Alves}, J., {Wisotzki}, L., {Kupko}, D.,
  {Quirrenbach}, A., {Bomans}, D., \& {Califa Collaboration}. 2013, \aap, 554,
  A58


\bibitem[{{S{\'a}nchez} {et~al.}(2011){S{\'a}nchez}, {Rosales-Ortega},
  {Kennicutt}, {Johnson}, {Diaz}, {Pasquali}, \& {Hao}}]{sanchez11}
{S{\'a}nchez}, S.~F., {Rosales-Ortega}, F.~F., {Kennicutt}, R.~C., {Johnson},
  B.~D., {Diaz}, A.~I., {Pasquali}, A., \& {Hao}, C.~N. 2011, \mnras, 410, 313


\bibitem[{{S{\'a}nchez} {et~al.}(2012{\natexlab{b}}){S{\'a}nchez},
  {Rosales-Ortega}, {Marino}, {Iglesias-P{\'a}ramo}, {V{\'{\i}}lchez},
  {Kennicutt}, {D{\'{\i}}az}, {Mast}, {Monreal-Ibero}, {Garc{\'{\i}}a-Benito},
  {Bland-Hawthorn}, {P{\'e}rez}, {Gonz{\'a}lez Delgado}, {Husemann},
  {L{\'o}pez-S{\'a}nchez}, {Cid Fernandes}, {Kehrig}, {Walcher}, {Gil de Paz},
  \& {Ellis}}]{sanchez12b}
{S{\'a}nchez}, S.~F., {Rosales-Ortega}, F.~F., {Marino}, R.~A.,
  {Iglesias-P{\'a}ramo}, J., {V{\'{\i}}lchez}, J.~M., {Kennicutt}, R.~C.,
  {D{\'{\i}}az}, A.~I., {Mast}, D., {Monreal-Ibero}, A.,
  {Garc{\'{\i}}a-Benito}, R., {Bland-Hawthorn}, J., {P{\'e}rez}, E.,
  {Gonz{\'a}lez Delgado}, R., {Husemann}, B., {L{\'o}pez-S{\'a}nchez},
  {\'A}.~R., {Cid Fernandes}, R., {Kehrig}, C., {Walcher}, C.~J., {Gil de Paz},
  A., \& {Ellis}, S. 2012{\natexlab{b}}, \aap, 546, A2


\bibitem[{{S{\'a}nchez-Bl{\'a}zquez} {et~al.}(2011){S{\'a}nchez-Bl{\'a}zquez},
  {Ocvirk}, {Gibson}, {P{\'e}rez}, \& {Peletier}}]{patri11}
{S{\'a}nchez-Bl{\'a}zquez}, P., {Ocvirk}, P., {Gibson}, B.~K., {P{\'e}rez}, I.,
  \& {Peletier}, R.~F. 2011, \mnras, 415, 709


\bibitem[{{S{\'a}nchez-Bl{\'a}zquez} {et~al.}(2006){S{\'a}nchez-Bl{\'a}zquez},
  {Peletier}, {Jim{\'e}nez-Vicente}, {Cardiel}, {Cenarro},
  {Falc{\'o}n-Barroso}, {Gorgas}, {Selam}, \& {Vazdekis}}]{miles}
{S{\'a}nchez-Bl{\'a}zquez}, P., {Peletier}, R.~F., {Jim{\'e}nez-Vicente}, J.,
  {Cardiel}, N., {Cenarro}, A.~J., {Falc{\'o}n-Barroso}, J., {Gorgas}, J.,
  {Selam}, S., \& {Vazdekis}, A. 2006, \mnras, 371, 703


\bibitem[{{S{\'a}nchez-Bl{\'a}zquez}
  {et~al.}(2014{\natexlab{a}}){S{\'a}nchez-Bl{\'a}zquez}, {Rosales-Ortega},
  {Diaz}, \& {S{\'a}nchez}}]{patri14a}
{S{\'a}nchez-Bl{\'a}zquez}, P., {Rosales-Ortega}, F., {Diaz}, A., \&
  {S{\'a}nchez}, S.~F. 2014{\natexlab{a}}, \mnras


\bibitem[{{S{\'a}nchez-Bl{\'a}zquez}
  {et~al.}(2014{\natexlab{b}}){S{\'a}nchez-Bl{\'a}zquez}, {Rosales-Ortega},
  {M{\'e}ndez-Abreu}, {P{\'e}rez}, {S{\'a}nchez}, {Zibetti}, {Aguerri},
  {Bland-Hawthorn}, {Catal{\'a}n-Torrecilla}, {Cid Fernandes}, {de Amorim}, {de
  Lorenzo-Caceres}, {Falc{\'o}n-Barroso}, {Galazzi}, {Garc{\'{\i}}a Benito},
  {Gil de Paz}, {Gonz{\'a}lez Delgado}, {Husemann}, {Iglesias-P{\'a}ramo},
  {Jungwiert}, {Marino}, {M{\'a}rquez}, {Mast}, {Mendoza}, {Moll{\'a}},
  {Papaderos}, {Ruiz-Lara}, {van de Ven}, {Walcher}, \& {Wisotzki}}]{patri14b}
{S{\'a}nchez-Bl{\'a}zquez}, P., {Rosales-Ortega}, F.~F., {M{\'e}ndez-Abreu},
  J., {P{\'e}rez}, I., {S{\'a}nchez}, S.~F., {Zibetti}, S., {Aguerri},
  J.~A.~L., {Bland-Hawthorn}, J., {Catal{\'a}n-Torrecilla}, C., {Cid
  Fernandes}, R., {de Amorim}, A., {de Lorenzo-Caceres}, A.,
  {Falc{\'o}n-Barroso}, J., {Galazzi}, A., {Garc{\'{\i}}a Benito}, R., {Gil de
  Paz}, A., {Gonz{\'a}lez Delgado}, R., {Husemann}, B., {Iglesias-P{\'a}ramo},
  J., {Jungwiert}, B., {Marino}, R.~A., {M{\'a}rquez}, I., {Mast}, D.,
  {Mendoza}, M.~A., {Moll{\'a}}, M., {Papaderos}, P., {Ruiz-Lara}, T., {van de
  Ven}, G., {Walcher}, C.~J., \& {Wisotzki}, L. 2014{\natexlab{b}}, \aap, 570,
  A6


\bibitem[{{Sarzi} {et~al.}(2006{\natexlab{a}}){Sarzi}, {Falc{\'o}n-Barroso},
  {Davies}, {Bacon}, {Bureau}, {Cappellari}, {de Zeeuw}, {Emsellem}, {Fathi},
  {Krajnovi{\'c}}, {Kuntschner}, {McDermid}, \& {Peletier}}]{sarzi2006}
{Sarzi}, M., {Falc{\'o}n-Barroso}, J., {Davies}, R.~L., {Bacon}, R., {Bureau},
  M., {Cappellari}, M., {de Zeeuw}, P.~T., {Emsellem}, E., {Fathi}, K.,
  {Krajnovi{\'c}}, D., {Kuntschner}, H., {McDermid}, R.~M., \& {Peletier},
  R.~F. 2006{\natexlab{a}}, \mnras, 366, 1151


\bibitem[{{Sarzi} {et~al.}(2006{\natexlab{b}}){Sarzi}, {Falc{\'o}n-Barroso},
  {Davies}, {Bacon}, {Bureau}, {Cappellari}, {de Zeeuw}, {Emsellem}, {Fathi},
  {Krajnovi{\'c}}, {Kuntschner}, {McDermid}, \& {Peletier}}]{sarzi06}
---. 2006{\natexlab{b}}, \mnras, 366, 1151


\bibitem[{{Serra} \& {Trager}(2007)}]{serra07}
{Serra}, P. \& {Trager}, S.~C. 2007, \mnras, 374, 769


\bibitem[{Stoklasov{\'a} {et~al.}(2009)Stoklasov{\'a}, Ferruit, Emsellem,
  Jungwiert, P{\'e}contal, \& S{\'a}nchez}]{Stoklasova:2009p3436}
Stoklasov{\'a}, I., Ferruit, P., Emsellem, E., Jungwiert, B., P{\'e}contal, E.,
  \& S{\'a}nchez, S.~F. 2009, A\&A, 500, 1287
 \href{http://adsabs.harvard.edu/cgi-bin/nph-data_query?bibcode=2009A\%2526A..%
.500.1287S&link_type=ABSTRACT}{\urllinklabel}

\bibitem[{Tinsley(1980)}]{Tinsley:1980p3431}
Tinsley, B.~M. 1980, FCPh, 5, 287
 \href{http://adsabs.harvard.edu/cgi-bin/nph-data_query?bibcode=1980FCPh....5.%
.287T&link_type=ABSTRACT}{\urllinklabel}

\bibitem[{{Tojeiro} {et~al.}(2007){Tojeiro}, {Heavens}, {Jimenez}, \&
  {Panter}}]{toje2007}
{Tojeiro}, R., {Heavens}, A.~F., {Jimenez}, R., \& {Panter}, B. 2007, \mnras,
  381, 1252


\bibitem[{{Tuffs} {et~al.}(2004){Tuffs}, {Popescu}, {V{\"o}lk}, {Kylafis}, \&
  {Dopita}}]{tuffs2004}
{Tuffs}, R.~J., {Popescu}, C.~C., {V{\"o}lk}, H.~J., {Kylafis}, N.~D., \&
  {Dopita}, M.~A. 2004, \aap, 419, 821


\bibitem[{{Vazdekis} {et~al.}(2010){Vazdekis}, {S{\'a}nchez-Bl{\'a}zquez},
  {Falc{\'o}n-Barroso}, {Cenarro}, {Beasley}, {Cardiel}, {Gorgas}, \&
  {Peletier}}]{vazdekis10}
{Vazdekis}, A., {S{\'a}nchez-Bl{\'a}zquez}, P., {Falc{\'o}n-Barroso}, J.,
  {Cenarro}, A.~J., {Beasley}, M.~A., {Cardiel}, N., {Gorgas}, J., \&
  {Peletier}, R.~F. 2010, \mnras, 404, 1639


\bibitem[{{Walcher} {et~al.}(2006){Walcher}, {B{\"o}ker}, {Charlot}, {Ho},
  {Rix}, {Rossa}, {Shields}, \& {van der Marel}}]{walch06}
{Walcher}, C.~J., {B{\"o}ker}, T., {Charlot}, S., {Ho}, L.~C., {Rix}, H.-W.,
  {Rossa}, J., {Shields}, J.~C., \& {van der Marel}, R.~P. 2006, \apj, 649, 692


\bibitem[{{Walcher} {et~al.}(2005){Walcher}, {van der Marel}, {McLaughlin},
  {Rix}, {B{\"o}ker}, {H{\"a}ring}, {Ho}, {Sarzi}, \& {Shields}}]{walcher05}
{Walcher}, C.~J., {van der Marel}, R.~P., {McLaughlin}, D., {Rix}, H.-W.,
  {B{\"o}ker}, T., {H{\"a}ring}, N., {Ho}, L.~C., {Sarzi}, M., \& {Shields},
  J.~C. 2005, \apj, 618, 237


\bibitem[{{Walcher} {et~al.}(2011){Walcher}, {Groves}, {Budav{\'a}ri}, \&
  {Dale}}]{walcher11}
{Walcher}, J., {Groves}, B., {Budav{\'a}ri}, T., \& {Dale}, D. 2011, \apss,
  331, 1


\bibitem[{{Wilkinson} {et~al.}(2015){Wilkinson}, {Maraston}, {Thomas},
  {Coccato}, {Tojeiro}, {Cappellari}, {Belfiore}, {Bershady}, {Blanton},
  {Bundy}, {Cales}, {Cherinka}, {Drory}, {Emsellem}, {Fu}, {Law}, {Li},
  {Maiolino}, {Masters}, {Tremonti}, {Wake}, {Wang}, {Weijmans}, {Xiao}, {Yan},
  {Zhang}, {Bizyaev}, {Brinkmann}, {Kinemuchi}, {Malanushenko}, {Malanushenko},
  {Oravetz}, {Pan}, \& {Simmons}}]{wilk15}
{Wilkinson}, D.~M., {Maraston}, C., {Thomas}, D., {Coccato}, L., {Tojeiro}, R.,
  {Cappellari}, M., {Belfiore}, F., {Bershady}, M., {Blanton}, M., {Bundy}, K.,
  {Cales}, S., {Cherinka}, B., {Drory}, N., {Emsellem}, E., {Fu}, H., {Law},
  D., {Li}, C., {Maiolino}, R., {Masters}, K., {Tremonti}, C., {Wake}, D.,
  {Wang}, E., {Weijmans}, A.-M., {Xiao}, T., {Yan}, R., {Zhang}, K., {Bizyaev},
  D., {Brinkmann}, J., {Kinemuchi}, K., {Malanushenko}, E., {Malanushenko}, V.,
  {Oravetz}, D., {Pan}, K., \& {Simmons}, A. 2015, \mnras, 449, 328


\bibitem[{Worthey(1994)}]{Worthey:1994p3434}
Worthey, G. 1994, ApJS, 95, 107
 \href{http://adsabs.harvard.edu/cgi-bin/nph-data_query?bibcode=1994ApJS...95.%
.107W&link_type=ABSTRACT}{\urllinklabel}

\end{thebibliography}